---
title: "Drawing Figure for manuscript"
author: "incheol, hyunsu"
date: "July 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data load
```{r, message=FALSE, warning=FALSE}
setwd("../Data_prep/divided_revised_data")

cre_na_omitted <- read.csv("cre_na_omitted.csv", row.names = "X")


Btrain		<- read.csv("Btrain.csv", row.names = "X")
Btrain.l	<- read.csv("Btrain_long.csv", header = T, row.names = "X")
Btrain.s	<- read.csv("Btrain_short.csv", header = T, row.names = "X")
Btrain.r	<- read.csv("Btrain_ramp.csv", header = T, row.names = "X")

Btest		<- read.csv("Btest.csv", row.names = "X")
Btest.l		<- read.csv("Btest_long.csv", header = T, row.names = "X")
Btest.s		<- read.csv("Btest_short.csv", header = T, row.names = "X")
Btest.r		<- read.csv("Btest_ramp.csv", header = T, row.names = "X")

Etrain		<- read.csv("Etrain.csv", row.names = "X")
Etrain.l	<- read.csv("Etrain_long.csv", header = T, row.names = "X")
Etrain.s	<- read.csv("Etrain_short.csv", header = T, row.names = "X")
Etrain.r	<- read.csv("Etrain_ramp.csv", header = T, row.names = "X")

Etest		<- read.csv("Etest.csv", row.names = "X")
Etest.l		<- read.csv("Etest_long.csv", header = T, row.names = "X")
Etest.s		<- read.csv("Etest_short.csv", header = T, row.names = "X")
Etest.r		<- read.csv("Etest_ramp.csv", header = T, row.names = "X")

Itrain		<- read.csv("Itrain.csv", row.names = "X")
Itrain.l	<- read.csv("Itrain_long.csv", header = T, row.names = "X")
Itrain.s	<- read.csv("Itrain_short.csv", header = T, row.names = "X")
Itrain.r	<- read.csv("Itrain_ramp.csv", header = T, row.names = "X")

Itest		<- read.csv("Itest.csv", row.names = "X")
Itest.l		<- read.csv("Itest_long.csv", header = T, row.names = "X")
Itest.s		<- read.csv("Itest_short.csv", header = T, row.names = "X")
Itest.r		<- read.csv("Itest_ramp.csv", header = T, row.names = "X")

Ltrain		<- read.csv("Ltrain.csv", row.names = "X")
Ltrain.l	<- read.csv("Ltrain_long.csv", header = T, row.names = "X")
Ltrain.s	<- read.csv("Ltrain_short.csv", header = T, row.names = "X")
Ltrain.r	<- read.csv("Ltrain_ramp.csv", header = T, row.names = "X")

Ltest		<- read.csv("Ltest.csv", row.names = "X")
Ltest.l		<- read.csv("Ltest_long.csv", header = T, row.names = "X")
Ltest.s		<- read.csv("Ltest_short.csv", header = T, row.names = "X")
Ltest.r		<- read.csv("Ltest_ramp.csv", header = T, row.names = "X")
```

# Data load(not merged Tg line)
```{r, message=FALSE, warning=FALSE}
setwd("../Data_prep/divided_revised_notmerged_data")

Etrain_n		<- read.csv("Etrain.csv", row.names = "X")
Etrain_n.l	<- read.csv("Etrain_long.csv", header = T, row.names = "X")
Etrain_n.s	<- read.csv("Etrain_short.csv", header = T, row.names = "X")
Etrain_n.r	<- read.csv("Etrain_ramp.csv", header = T, row.names = "X")

Etest_n		<- read.csv("Etest.csv", row.names = "X")
Etest_n.l		<- read.csv("Etest_long.csv", header = T, row.names = "X")
Etest_n.s		<- read.csv("Etest_short.csv", header = T, row.names = "X")
Etest_n.r		<- read.csv("Etest_ramp.csv", header = T, row.names = "X")

Itrain_n		<- read.csv("Itrain.csv", row.names = "X")
Itrain_n.l	<- read.csv("Itrain_long.csv", header = T, row.names = "X")
Itrain_n.s	<- read.csv("Itrain_short.csv", header = T, row.names = "X")
Itrain_n.r	<- read.csv("Itrain_ramp.csv", header = T, row.names = "X")

Itest_n		<- read.csv("Itest.csv", row.names = "X")
Itest_n.l		<- read.csv("Itest_long.csv", header = T, row.names = "X")
Itest_n.s		<- read.csv("Itest_short.csv", header = T, row.names = "X")
Itest_n.r		<- read.csv("Itest_ramp.csv", header = T, row.names = "X")

```


# make function for split vion plot
* https://stackoverflow.com/questions/35717353/split-violin-plot-with-ggplot2

```{r, message=FALSE, warning=FALSE}
require(ggplot2)
GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, draw_group = function(self, data, ..., draw_quantiles = NULL){
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1,'group']
  newdata <- plyr::arrange(transform(data, x = if(grp%%2==1) xminv else xmaxv), if(grp%%2==1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1,nrow(newdata)-1,nrow(newdata)), 'x'] <- round(newdata[1, 'x']) 
  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 
                                              1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function (mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, position = position, show.legend = show.legend, inherit.aes = inherit.aes, params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}
```

# Draw figure2 split violin plots

```{r, message=FALSE, warning=FALSE}
require(ggplot2)
require(reshape2)
require(latex2exp)
require(gridExtra)


fig2data <- subset(cre_na_omitted, select = -c(specimen_id, transgenic_line, 
                                              layer_full, acronym))
fig2meltdata <- melt(fig2data, id = c("binary_neuron"))

levels(fig2meltdata$variable)


levels(fig2meltdata$variable) <- c("$\\Alpha_{index}$", "$\\ISI_{avg}$", 
                                   "$\\FR/I$", "$\\t^{long}_{FT}$", 
                                   "$\\t^{ramp}_{FT}$", "$\\t^{short}_{FT}$",
                                   "$\\V^{long}_{FT}$", "$\\V^{ramp}_{FT}$",
                                   "$\\V^{short}_{FT}$", "$\\t^{long}_{lat}$",
                                   "$\\t^{long}_{P}$", "$\\t^{ramp}_{P}$",
                                   "$\\t^{short}_{P}$", "$\\V^{long}_{P}$",
                                   "$\\V^{ramp}_{P}$", "$\\V^{short}_{P}$", 
                                   "$\\R_{input}$", "$\\Sag$", 
                                   "$\\I^{long}_{\\Theta}$", "$\\I^{ramp}_{\\Theta}$",
                                   "$\\I^{short}_{\\Theta}$", "$\\t^{long}_{\\Theta}$",
                                   "$\\t^{ramp}_{\\Theta}$", "$\\t^{short}_{\\Theta}$",
                                   "$\\V^{long}_{\\Theta}$", "$\\V^{ramp}_{\\Theta}$",
                                   "$\\V^{short}_{\\Theta}$", "$\\t^{long}_{T}$",
                                   "$\\t^{ramp}_{T}$", "$\\t^{short}_{T}$",
                                   "$\\V^{long}_{T}$", "$\\V^{ramp}_{T}$",
                                   "$\\V^{short}_{T}$",  "$\\rho^{long}$", 
                                   "$\\rho^{ramp}$", "$\\rho^{short}$", 
                                   "$\\V_{rest}$", "$\\tau$",
                                   "$\\FR", "$\\H^{short}$",
                                   "$\\H^{long}$", "$\\H^{ramp}$")

# 1st row of figure2(mV)
v_filter <-fig2meltdata[grep("V", fig2meltdata$variable), ]
v_filter_wo_p <- v_filter[grep("[^P]\\}\\$$", v_filter$variable), ]

fig2_11 <- ggplot(data = v_filter_wo_p, 
                  aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") +labs(x = "", y = "mV") +
   scale_x_discrete(labels = parse(text = TeX(unique(v_filter_wo_p$variable)))) + 
  theme(axis.title.y = element_text(size = rel(0.7))) 

sag <- fig2meltdata[grep("Sag\\$", fig2meltdata$variable), ]
fig2_12 <- ggplot(data = sag, 
                  aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "right") + 
  labs(x = "", y = "") +
  scale_x_discrete(labels = parse(text =TeX(unique(sag$variable)))) + 
  theme(axis.title.y = element_text(size = rel(0.7))) + 
  scale_fill_discrete(name = "", labels = c("E", "I")) +
  theme(legend.text = element_text(size = rel(0.5)))

fig2_1 <- grid.arrange(fig2_11, fig2_12, widths = c(10, 2), nrow = 1)

# https://chemicalstatistician.wordpress.com/2018/03/10/use-unique-instead-of-levels-to-find-the-possible-values-of-a-character-variable-in-r/


# 2nd row of figure2(mV, ratio, resistance)
over_zero_v_filter <- rbind(v_filter[grep("P", v_filter$variable), ],
                       fig2meltdata[grep("H", fig2meltdata$variable), ])
fig2_21 <- ggplot(data = over_zero_v_filter, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "mV") +
   scale_x_discrete(labels = parse(text = TeX(unique(over_zero_v_filter$variable)))) + theme(axis.title.y = element_text(size = rel(0.7)))

up_d_ratio <- fig2meltdata[grep("rho", fig2meltdata$variable), ]
fig2_22 <- ggplot(data = up_d_ratio, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "") +
  scale_x_discrete(labels = parse(text = TeX(unique(up_d_ratio$variable)))) + theme(axis.title.y = element_text(size = rel(0.7)))

adaptation <- fig2meltdata[grep("inde", fig2meltdata$variable), ]
fig2_23 <- ggplot(data = adaptation, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "") + 
  scale_x_discrete(labels = parse(text =TeX(unique(adaptation$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

tau <- fig2meltdata[grep("tau\\$", fig2meltdata$variable), ]
fig2_24 <- ggplot(data = tau, 
                  aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + 
  labs(x = "", y = "ms") +
  scale_x_discrete(labels = parse(text =TeX(unique(tau$variable)))) + 
  theme(axis.title.y = element_text(size = rel(0.7))) 


resist <- fig2meltdata[grep("[^F]R", fig2meltdata$variable), ]
fig2_25 <- ggplot(data = resist, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = TeX('$\\M\\Omega$')) +
  scale_x_discrete(labels = parse(text =TeX(unique(resist$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

fig2_2 <- grid.arrange(fig2_21, fig2_22, fig2_23, fig2_24, fig2_25, widths = c(5,3,2,1.5,2), nrow = 1)

# 3rd row of figure2(ms, firing)
t_long_filter <- rbind(fig2meltdata[grep("t\\^\\{long\\}_\\{[^l]", 
                                         fig2meltdata$variable) ,],
                       fig2meltdata[grep("t\\^\\{short\\}_\\{T", 
                                         fig2meltdata$variable), ] )


fig2_31 <- ggplot(data = t_long_filter, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() +theme(legend.position = "none") + labs(x= "", y = "mS") +
  scale_x_discrete(labels = parse(text =TeX(unique(t_long_filter$variable)))) + theme(axis.title.y = element_text(size = rel(0.7)))

latency <- fig2meltdata[grep("lat", fig2meltdata$variable), ]
fig2_32 <- ggplot(data = latency, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "S") +
  scale_x_discrete(labels = parse(text =TeX(unique(latency$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

avg_isi <- fig2meltdata[grep("avg", fig2meltdata$variable), ]
fig2_33 <- ggplot(data = avg_isi, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "mS") +
  scale_x_discrete(labels = parse(text =TeX(unique(avg_isi$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

firing_rate <- fig2meltdata[grep("FR$", fig2meltdata$variable), ]
fig2_34 <- ggplot(data = firing_rate, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "spikes/s") +
  scale_x_discrete(labels = parse(text =TeX(unique(firing_rate$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

f_i_curve <- fig2meltdata[grep("FR/", fig2meltdata$variable), ]
fig2_35 <- ggplot(data = f_i_curve, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "spikes/s/pA") +
  scale_x_discrete(labels = parse(text =TeX(unique(f_i_curve$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

fig2_3 <- grid.arrange(fig2_31, fig2_32, fig2_33, fig2_34, fig2_35, widths = c(6,1.5, 1.5, 1.5, 1.5), nrow=1)



# 4th row of figure2(ms, pA)
t_filter <- fig2meltdata[grep("t\\^\\{short", fig2meltdata$variable), ]

t_short_filter_all <- rbind(t_filter[grep("FT\\}\\$$", t_filter$variable), ], 
                        t_filter[grep("[^T]\\}\\$$", t_filter$variable), ])

t_short_filter <- subset(t_short_filter_all, 0 < value & value < 12)

fig2_41 <- ggplot(data = t_short_filter, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x= "", y = "mS") +
  scale_x_discrete(labels = parse(text =TeX(unique(t_short_filter$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

t_ramp_filter <- fig2meltdata[grep("t\\^\\{ramp", fig2meltdata$variable), ]
fig2_42 <- ggplot(data = t_ramp_filter, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + theme(legend.position = "none") + labs(x = "", y = "ms") +
  scale_x_discrete(labels = parse(text =TeX(unique(t_ramp_filter$variable)))) +theme(axis.title.y = element_text(size = rel(0.7)))

i_filter <- fig2meltdata[grep("I\\^", fig2meltdata$variable), ]
fig2_43 <- ggplot(data = i_filter, aes(x = variable, y = value, fill = binary_neuron)) + 
  geom_split_violin() + theme_minimal() + scale_y_log10() + theme(legend.position = "none") + labs(x = "", y = "pA") +
  scale_x_discrete(labels = parse(text =TeX(unique(i_filter$variable)))) +theme(axis.title.y = element_text(size = rel(0.7))) 

fig2_4 <- grid.arrange(fig2_41, fig2_42, fig2_43, widths = c(3,4,3), nrow = 1)

# arrange violin plots
fig2_l <- grid.arrange(fig2_1, fig2_2, fig2_3, fig2_4, ncol = 1)

# for heatmap, correlation matrix

fig2data_numeric <- subset(fig2data, select = -c(binary_neuron))

colnames(fig2data_numeric) <- c("$\\Alpha_{index}$", "$\\ISI_{avg}$", 
                                   "$\\FR/I$", "$\\t^{long}_{FT}$", 
                                   "$\\t^{ramp}_{FT}$", "$\\t^{short}_{FT}$",
                                   "$\\V^{long}_{FT}$", "$\\V^{ramp}_{FT}$",
                                   "$\\V^{short}_{FT}$", "$\\t^{long}_{lat}$",
                                   "$\\t^{long}_{P}$", "$\\t^{ramp}_{P}$",
                                   "$\\t^{short}_{P}$", "$\\V^{long}_{P}$",
                                   "$\\V^{ramp}_{P}$", "$\\V^{short}_{P}$", 
                                   "$\\R_{input}$", "$\\Sag$", 
                                   "$\\I^{long}_{\\Theta}$", "$\\I^{ramp}_{\\Theta}$",
                                   "$\\I^{short}_{\\Theta}$", "$\\t^{long}_{\\Theta}$",
                                   "$\\t^{ramp}_{\\Theta}$", "$\\t^{short}_{\\Theta}$",
                                   "$\\V^{long}_{\\Theta}$", "$\\V^{ramp}_{\\Theta}$",
                                   "$\\V^{short}_{\\Theta}$", "$\\t^{long}_{T}$",
                                   "$\\t^{ramp}_{T}$", "$\\t^{short}_{T}$",
                                   "$\\V^{long}_{T}$", "$\\V^{ramp}_{T}$",
                                   "$\\V^{short}_{T}$",  "$\\rho^{long}$", 
                                   "$\\rho^{ramp}$", "$\\rho^{short}$", 
                                   "$\\V_{rest}$", "$\\tau$",
                                   "$\\FR", "$\\H^{short}$",
                                   "$\\H^{long}$", "$\\H^{ramp}$")



cormat_posneg <- cor(fig2data_numeric)

cormat <- abs(cormat_posneg) 
reorder_cormat <- function(cormat){
# Use correlation between variables as distance
   dd <- as.dist((1-cormat))
   hc <- hclust(dd, method = "centroid")
   cormat <-cormat[hc$order, hc$order]
}

cormat <- reorder_cormat(cormat)
melted_fig2b<-melt(cormat)
melted_fig2b$Var1 <- factor(melted_fig2b$Var1, levels=unique(as.character(melted_fig2b$Var1)))
melted_fig2b$Var2 <- factor(melted_fig2b$Var2, levels=unique(as.character(melted_fig2b$Var2)))
fig2_r <- ggplot(data=melted_fig2b, aes(Var1, Var2, fill=value)) + 
      geom_tile() + scale_fill_gradient2(low = "darkolivegreen4", high = "firebrick2", mid = "lightgoldenrodyellow", 
                    midpoint = 0, limit = c(0,1), space = "Lab", name="r") +
      labs(x = "", y = "")+
      theme(legend.position = "bottom") + 
      scale_y_discrete(position = "right", labels = parse(text =TeX(unique(melted_fig2b$Var1)))) + 
      theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.ticks.y = element_blank()) +
      theme(axis.title.y = element_text(size = rel(0.7)))

# fig2<- grid.arrange(fig2_l, fig2_r, widths = c(1.6,1), nrow = 1)

# ggsave("fig2.tiff",fig2, width=11, height=7, units ="in", dpi = 300)
ggsave("fig2_revised.tiff", fig2_l, width = 11, height = 7, units = "in", dpi = 300)
ggsave("SF1_heatmap.tiff", fig2_r, width = 7, height = 7, units = "in", dpi = 300)

```


# redraw pie chart(figure3) to cumulative bar chart.
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
require(gridExtra)

Btrain_freq <- as.data.frame(prop.table(table(Btrain$binary)))
Btest_freq <- as.data.frame(prop.table(table(Btest$binary)))
Btrain_freq <- cbind(Btrain_freq, 'train')
Btest_freq <- cbind(Btest_freq, 'test')
colnames(Btrain_freq) <- c("neuron", "probability", "set")
colnames(Btest_freq) <- c("neuron", "probability", "set")
Bpro <- rbind(Btrain_freq, Btest_freq)

fig3_1 <- ggplot(Bpro, aes(x = set, y = probability, fill = neuron)) + 
  geom_bar(stat="identity") + # for cumulative bar graph
  theme_minimal() + scale_fill_brewer(type = "seq", palette = "Paired") +
  labs(x = "", y = "", fill = "") + 
  coord_flip() + scale_x_discrete(limits = rev(levels(Bpro$set))) + # xy axis swap and reverse order of set
  theme(legend.position = "top", axis.text.x = element_blank())


levels(Etest_n$transgenic_line) <- levels(Etrain_n$transgenic_line)

Etrain_n_freq <- as.data.frame(prop.table(table(Etrain_n$transgenic_line)))
Etest_n_freq <- as.data.frame(prop.table(table(Etest_n$transgenic_line)))
Etrain_n_freq <- cbind(Etrain_n_freq, 'train')
Etest_n_freq <- cbind(Etest_n_freq, 'test')
colnames(Etrain_n_freq) <- c("neuron", "probability", "set")
colnames(Etest_n_freq) <- c("neuron", "probability", "set")
Epro_n <- rbind(Etrain_n_freq, Etest_n_freq)

fig3_2 <- ggplot(Epro_n, aes(x = set, y = probability, fill = neuron)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + scale_fill_brewer(type = "seq", palette = "Spectral") +
  labs(x = "", y = "", fill  = "excitatory line") + 
  coord_flip() + scale_x_discrete(limits = rev(levels(Epro_n$set))) + 
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.y = element_blank())

levels(Etrain$transgenic_line) <- c("Ctgf-T2A-dgCre", "Cux&Slc17a6", "Nr5a1&Scnn1a", 
                                    "Ntsr1-Cre_GN220", "Rbp4-Cre_KL100", "Rorb-IRES2-Cre")
levels(Etest$transgenic_line) <- c("Ctgf-T2A-dgCre", "Cux&Slc17a6", "Nr5a1&Scnn1a", 
                                    "Ntsr1-Cre_GN220", "Rbp4-Cre_KL100", "Rorb-IRES2-Cre")

Etrain_freq <- as.data.frame(prop.table(table(Etrain$transgenic_line)))
Etest_freq <- as.data.frame(prop.table(table(Etest$transgenic_line)))
Etrain_freq <- cbind(Etrain_freq, 'train')
Etest_freq <- cbind(Etest_freq, 'test')
colnames(Etrain_freq) <- c("neuron", "probability", "set")
colnames(Etest_freq) <- c("neuron", "probability", "set")
Epro <- rbind(Etrain_freq, Etest_freq)

fig3_3 <- ggplot(Epro, aes(x = set, y = probability, fill = neuron)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + scale_fill_brewer(type = "seq", palette = "Spectral") +
  labs(x = "", y = "", fill  = "excitatory line") + 
  coord_flip() + scale_x_discrete(limits = rev(levels(Epro_n$set))) + 
  theme(legend.position = "top", axis.text.x = element_blank(), axis.ticks.y = element_blank())


Itrain_n_freq <- as.data.frame(prop.table(table(Itrain_n$transgenic_line)))
Itest_n_freq <- as.data.frame(prop.table(table(Itest_n$transgenic_line)))
Itrain_n_freq <- cbind(Itrain_n_freq, 'train')
Itest_n_freq <- cbind(Itest_n_freq, 'test')
colnames(Itrain_n_freq) <- c("neuron", "probability", "set")
colnames(Itest_n_freq) <- c("neuron", "probability", "set")
Ipro_n <- rbind(Itrain_n_freq, Itest_n_freq)

fig3_4 <- ggplot(Ipro_n, aes(x = set, y = probability, fill = neuron)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + scale_fill_brewer(type = "seq", palette = "Spectral") +
  labs(x = "", fill = "inhibitory line") + 
  coord_flip() + scale_x_discrete(limits = rev(levels(Ipro_n$set))) + 
  theme(legend.position = "top", axis.ticks.y = element_blank())


Itrain_freq <- as.data.frame(prop.table(table(Itrain$transgenic_line)))
Itest_freq <- as.data.frame(prop.table(table(Itest$transgenic_line)))
Itrain_freq <- cbind(Itrain_freq, 'train')
Itest_freq <- cbind(Itest_freq, 'test')
colnames(Itrain_freq) <- c("neuron", "probability", "set")
colnames(Itest_freq) <- c("neuron", "probability", "set")
Ipro <- rbind(Itrain_freq, Itest_freq)

fig3_5 <- ggplot(Ipro, aes(x = set, y = probability, fill = neuron)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + scale_fill_brewer(type = "seq", palette = "Spectral") +
  labs(x = "", fill = "inhibitory line") + 
  coord_flip() + scale_x_discrete(limits = rev(levels(Ipro_n$set))) + 
  theme(legend.position = "top", axis.ticks.y = element_blank())

levels(Ltrain$L_tg) <- c("L2/3_Cre", "L4_Cre", "L5_Cre", "L6a_Cre", "L6b_Cre")
levels(Ltest$L_tg) <- c("L2/3_Cre", "L4_Cre", "L5_Cre", "L6a_Cre", "L6b_Cre")

Ltrain_freq <- as.data.frame(prop.table(table(Ltrain$L_tg)))
Ltest_freq <- as.data.frame(prop.table(table(Ltest$L_tg)))
Ltrain_freq <- cbind(Ltrain_freq, 'train')
Ltest_freq <- cbind(Ltest_freq, 'test')
colnames(Ltrain_freq) <- c("neuron", "probability", "set")
colnames(Ltest_freq) <- c("neuron", "probability", "set")
Lpro <- rbind(Ltrain_freq, Ltest_freq)

fig3_6 <- ggplot(Lpro, aes(x = set, y = probability, fill = neuron)) + 
  geom_bar(stat="identity") + 
  theme_minimal() + scale_fill_brewer(type = "seq", palette = "Spectral") +
  labs(x = "", fill = "layer location of excitary neuron restricted to Cre") + 
  coord_flip() + scale_x_discrete(limits = rev(levels(Ipro_n$set))) + 
  theme(legend.position = "top", axis.ticks.y = element_blank())

fig3_6

fig3 <- grid.arrange(fig3_1, fig3_2, fig3_3, fig3_4, fig3_5, fig3_6, ncol = 1)

ggsave("SF2.tiff", fig3, width = 10, height = 10, units = "in", dpi = 300)
```

# Binary classification

## Load ANN results
```{r, message=FALSE, warning=FALSE}
setwd("../ANN/revised_results")
B.ANN.full <-read.csv("00_4_binary_full_ANNmodel_prob.csv",header=F) 
B.ANN.long <-read.csv("01_4_binary_long_ANNmodel_prob.csv",header=F)
B.ANN.short<-read.csv("02_4_binary_short_ANNmodel_prob.csv",header=F)
B.ANN.ramp <-read.csv("03_4_binary_ramp_ANNmodel_prob.csv",header=F)

E.ANN.full <-read.csv("04_4_Eline_full_argmax.csv",header=F) 
E.ANN.long <-read.csv("05_4_Eline_long_argmax.csv",header=F)
E.ANN.short<-read.csv("06_4_Eline_short_argmax.csv",header=F)
E.ANN.ramp <-read.csv("07_4_Eline_ramp_argmax.csv",header=F)

I.ANN.full <-read.csv("08_4_Iline_full_argmax.csv",header=F) 
I.ANN.long <-read.csv("09_4_Iline_long_argmax.csv",header=F)
I.ANN.short<-read.csv("10_4_Iline_short_argmax.csv",header=F)
I.ANN.ramp <-read.csv("11_4_Iline_ramp_argmax.csv",header=F)

L.ANN.full <-read.csv("12_4_Lline_full_argmax.csv",header=F) 
L.ANN.long <-read.csv("13_4_Lline_long_argmax.csv",header=F)
L.ANN.short<-read.csv("14_4_Lline_short_argmax.csv",header=F)
L.ANN.ramp <-read.csv("15_4_Lline_ramp_argmax.csv",header=F)
```

# Load LASSO and RF models
```{r, message=FALSE, warning=FALSE}
setwd("../lasso_rf/")

model_files <- list.files("./R_models/")

for (file_name in model_files){
  load(paste0("./R_models/",file_name))
} 


```


# Draw Figure 4 classification E vs I, ROC curves and accuracy bar plot
https://stackoverflow.com/questions/24303203/creating-roc-curve-with-ggplot
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
library(ROCR)
library(magrittr)
library(caret)
require(gridExtra)
library(latex2exp)


# Making conventional ROC curve by detemining by firing_rate.

x.conven <- cre_na_omitted$firing_rate
preds = (x.conven-min(x.conven))/(max(x.conven)-min(x.conven))

conventional.pred = prediction(preds, cre_na_omitted$binary_neuron, label.ordering = c("Excitatory", "Inhibitory"))
FR_ROC <- cbind(performance(conventional.pred,"tpr","fpr")@x.values[[1]], performance(conventional.pred,"tpr","fpr")@y.values[[1]])
FR_ROC <- cbind.data.frame(FR_ROC, c("FR"))
colnames(FR_ROC) <- c("fpr", "tpr", "model")
FR_auc  = round(performance(conventional.pred,"auc")@y.values[[1]], digits = 4)


# Making ROC curve determined by Rho
rho_short <- cre_na_omitted$upstroke_downstroke_ratio_short_square
rho_long <- cre_na_omitted$upstroke_downstroke_ratio_long_square
rho_ramp <- cre_na_omitted$upstroke_downstroke_ratio_ramp

preds_rho_short = (rho_short-min(rho_short))/(max(rho_short)-min(rho_short))
preds_rho_long = (rho_long-min(rho_long))/(max(rho_long)-min(rho_long))
preds_rho_ramp = (rho_ramp-min(rho_ramp))/(max(rho_ramp)-min(rho_ramp))

short_predicted = prediction(preds_rho_short, cre_na_omitted$binary_neuron, label.ordering = c("Inhibitory", "Excitatory"))
long_predicted = prediction(preds_rho_long, cre_na_omitted$binary_neuron, label.ordering = c("Inhibitory", "Excitatory"))
ramp_predicted = prediction(preds_rho_ramp, cre_na_omitted$binary_neuron, label.ordering = c("Inhibitory", "Excitatory"))



rho_short_ROC <- cbind(performance(short_predicted,"tpr","fpr")@x.values[[1]], 
                 performance(short_predicted,"tpr","fpr")@y.values[[1]])
rho_long_ROC <- cbind(performance(long_predicted,"tpr","fpr")@x.values[[1]], 
                 performance(long_predicted,"tpr","fpr")@y.values[[1]])
rho_ramp_ROC <- cbind(performance(ramp_predicted,"tpr","fpr")@x.values[[1]], 
                 performance(ramp_predicted,"tpr","fpr")@y.values[[1]])

rho_short_ROC <- cbind.data.frame(rho_short_ROC, c("rho_short"))
rho_long_ROC <- cbind.data.frame(rho_long_ROC, c("rho_long"))
rho_ramp_ROC <- cbind.data.frame(rho_ramp_ROC, c("rho_ramp"))

colnames(rho_short_ROC) <- c("fpr", "tpr", "model")
colnames(rho_long_ROC) <- c("fpr", "tpr", "model")
colnames(rho_ramp_ROC) <- c("fpr", "tpr", "model")

rho_short_auc  = round(performance(short_predicted,"auc")@y.values[[1]], digits = 4)
rho_long_auc  = round(performance(long_predicted,"auc")@y.values[[1]], digits = 4)
rho_ramp_auc  = round(performance(ramp_predicted,"auc")@y.values[[1]], digits = 4)

BrocANN <- function(model) {
    pred = prediction(model[,1],Btest$binary_neuron)
    fpr = performance(pred,"tpr","fpr")@x.values[[1]]
    tpr = performance(pred,"tpr","fpr")@y.values[[1]]
    ROC = cbind(fpr, tpr)
    ROCs = cbind.data.frame(ROC, paste(substitute(model)))
    colnames(ROCs) = c("fpr", "tpr", "model")
    auc = round(performance(pred, "auc")@y.values[[1]], digits = 4)
    results = list("ROC" = ROCs, "AUC" = auc)
    return(results)
}

Broc <- function(model, dataset) {
     pred_ = predict(model, type="prob", newdata=dataset)[,2]
     pred = prediction(pred_, Btest$binary_neuron)
     fpr = performance(pred,"tpr","fpr")@x.values[[1]]
     tpr = performance(pred,"tpr","fpr")@y.values[[1]]
     ROC = cbind(fpr, tpr)
     ROCs = cbind.data.frame(ROC, paste(substitute(model)))
     colnames(ROCs) = c("fpr", "tpr", "model")
     auc = round(performance(pred, "auc")@y.values[[1]], digits = 4)
     results = list("ROC" = ROCs, "AUC" = auc)
     return(results)
}

ANN_full_ROC <- BrocANN(B.ANN.full)$ROC
reg_full_ROC <- Broc(B.reg.full.nocv, Btest)$ROC
rf_full_ROC <- Broc(B.rf.full.nocv, Btest)$ROC


full_ROC <- rbind(ANN_full_ROC, reg_full_ROC, rf_full_ROC, rho_ROC)

 
levels(full_ROC$model) <- c(paste0("ANN(", BrocANN(B.ANN.full)$AUC, ")"),
                            paste0("LASSO(", Broc(B.reg.full.nocv, Btest)$AUC, ")"),
                            paste0("RF(", Broc(B.rf.full.nocv, Btest)$AUC, ")"),
                            paste0("$\\rho^{short}$(", rho_short_auc, ")"))

fig4_1 <- ggplot(data=full_ROC, aes(fpr, tpr, color = model)) + geom_line() +
               geom_abline(aes(intercept=0, slope=1), linetype="dashed") +
               theme_classic() + 
               labs(title = "Full", x = "FPR(1-specificity)", y = "TPR(sensitivity)") +
               theme(legend.position = c(1, 0.01), 
                     legend.justification = c("right", "bottom"), 
                     legend.box.just = c("right", "bottom"), 
                     legend.text.align = 1, 
                     legend.title = element_blank(), 
                     plot.title = element_text(hjust = 0.5)) +
               scale_color_brewer(palette = "Set1", 
                                  labels = parse(text =TeX(unique(full_ROC$model)))) 
fig4_1

ANN_long_ROC <- BrocANN(B.ANN.long)$ROC
reg_long_ROC <- Broc(B.reg.long.nocv, Btest)$ROC
rf_long_ROC <- Broc(B.rf.long.nocv, Btest)$ROC
long_ROC <- rbind(ANN_long_ROC, reg_long_ROC, rf_long_ROC, rho_long_ROC)

levels(long_ROC$model) <- c(paste0("ANN(", BrocANN(B.ANN.long)$AUC, ")"),
                            paste0("LASSO(", Broc(B.reg.long.nocv, Btest)$AUC, ")"),
                            paste0("RF(", Broc(B.rf.long.nocv, Btest)$AUC, ")"),
                            paste0("$\\rho^{long}$(", rho_long_auc, ")"))

fig4_2 <- ggplot(data = long_ROC, aes(fpr, tpr, color = model)) + geom_line() +
               geom_abline(aes(intercept=0, slope=1), linetype="dashed") +
               theme_classic() + 
               labs(title = "Long", x = "FPR(1-specificity)", y = "TPR(sensitivity)") +
               theme(legend.position = c(1, 0.01), 
                     legend.justification = c("right", "bottom"), 
                     legend.box.just = c("right", "bottom"), 
                     legend.text.align = 1,
                     legend.title = element_blank(), 
                     plot.title = element_text(hjust = 0.5)) +
               scale_color_brewer( palette = "Set1", 
                                   labels = parse(text =TeX(unique(long_ROC$model))))

ANN_short_ROC <- BrocANN(B.ANN.short)$ROC
reg_short_ROC <- Broc(B.reg.short.nocv, Btest)$ROC
rf_short_ROC <- Broc(B.rf.short.nocv, Btest)$ROC
short_ROC <- rbind(ANN_short_ROC, reg_short_ROC, rf_short_ROC, rho_short_ROC)

levels(short_ROC$model) <- c(paste0("ANN(", BrocANN(B.ANN.short)$AUC, ")"),
                            paste0("LASSO(", Broc(B.reg.short.nocv, Btest)$AUC, ")"),
                            paste0("RF(", Broc(B.rf.short.nocv, Btest)$AUC, ")"),
                            paste0("$\\rho^{short}$(", rho_short_auc, ")"))

fig4_3 <- ggplot(data = short_ROC, aes(fpr, tpr, color = model)) + geom_line() +
               geom_abline(aes(intercept=0, slope=1), linetype="dashed") +
               theme_classic() + 
               labs(title = "Short", x = "FPR(1-specificity)", y = "TPR(sensitivity)") +
               theme(legend.position = c(1, 0.01), 
                     legend.justification = c("right", "bottom"), 
                     legend.box.just = c("right", "bottom"), 
                     legend.text.align = 1,
                     legend.title = element_blank(), 
                     plot.title = element_text(hjust = 0.5)) +
               scale_color_brewer( palette = "Set1",
                                   labels = parse(text =TeX(unique(short_ROC$model))))

ANN_ramp_ROC <- BrocANN(B.ANN.ramp)$ROC
reg_ramp_ROC <- Broc(B.reg.ramp.nocv, Btest)$ROC
rf_ramp_ROC <- Broc(B.rf.ramp.nocv, Btest)$ROC
ramp_ROC <- rbind(ANN_ramp_ROC, reg_ramp_ROC, rf_ramp_ROC, rho_ramp_ROC)

levels(ramp_ROC$model) <- c(paste0("ANN(", BrocANN(B.ANN.ramp)$AUC, ")"),
                            paste0("LASSO(", Broc(B.reg.ramp.nocv, Btest)$AUC, ")"),
                            paste0("RF(", Broc(B.rf.ramp.nocv, Btest)$AUC, ")"),
                            paste0("$\\rho^{ramp}$(", rho_ramp_auc, ")"))



fig4_4 <- ggplot(data = ramp_ROC, aes(fpr, tpr, color = model)) + geom_line() + 
              geom_abline(aes(intercept=0, slope=1), linetype="dashed") +
               theme_classic() + 
               labs(title = "Ramp", x = "FPR(1-specificity)", y = "TPR(sensitivity)") +
               theme(legend.position = c(1, 0.01), 
                     legend.justification = c("right", "bottom"), 
                     legend.box.just = c("right", "bottom"), 
                     legend.text.align = 1, 
                     legend.title = element_blank(), 
                     plot.title = element_text(hjust = 0.5)) +
               scale_color_brewer( palette = "Set1",
                                   labels = parse(text =TeX(unique(ramp_ROC$model))))

fig4t <- grid.arrange(fig4_1, fig4_2, fig4_3, fig4_4, ncol = 2)

ggsave("fig4t.tiff", fig4t, width = 7, height = 7, units = "in", dpi = 300)


# drawing error bargraph for accuracy performance

models <- c("ANN", "reg", "rf")
input <- c("full", "long", "short", "ramp")

accu_binary <- NA

for(i in 1:3) {
  if (models[i] == "ANN") {
    for(j in 1:4) {
      modelname <- paste0("B.",models[i],".",input[j])
      model <- get(modelname)
      accu <- confusionMatrix(as.factor(round(model[,1]) + 1), as.factor(as.integer(Btest$binary_neuron)))
      accu_each <- as.data.frame(accu$overall[c(1, 3:4)])
      accu_each <- rbind.data.frame(accu_each, models[i], input[j])
      colnames(accu_each) <- modelname
      accu_binary <- cbind.data.frame(accu_binary, accu_each)
      
      }
    }
  else {
      for(j in 1:4) {
        modelname <- (paste0("B.",models[i], ".", input[j],".nocv"))
        model <- get(modelname)
        accu <- confusionMatrix(predict(model, newdata = Btest), Btest$binary_neuron)
        accu_each <- as.data.frame(accu$overall[c(1, 3:4)])
        accu_each <- rbind.data.frame(accu_each, models[i], input[j])
        colnames(accu_each) <- modelname
        accu_binary <- cbind.data.frame(accu_binary, accu_each)
        }
  }
}


rho_CM <- confusionMatrix(as.factor(abs(round(preds_rho_long)-1)+1),   as.factor(as.integer(cre_na_omitted$binary_neuron))) # the ordering of labelling switched
rho_Accu <- rho_CM$overall[c(1,3:4)]

accu_binary <- cbind.data.frame(accu_binary[2:13])
accu_binary <- as.data.frame(t(accu_binary))
colnames(accu_binary) <- c("Accuracy", "LowCI", "UpCI", "Model", "Input")
accu_binary$Accuracy <- as.numeric(as.character(accu_binary$Accuracy))
accu_binary$LowCI <- as.numeric(as.character(accu_binary$LowCI))
accu_binary$UpCI <- as.numeric(as.character(accu_binary$UpCI))
accu_binary$Input <- factor(accu_binary$Input, levels(accu_binary$Input)[c(1,2,4,3)]) # reorder levels of input from alphabetical to experimental, to match with previous curves
levels(accu_binary$Model) <- c("ANN", "LASSO", "RF")
levels(accu_binary$Input) <- c("Full", "Long", "Short", "Ramp")

fig4b <- ggplot(data = accu_binary, aes(Input, Accuracy, fill = Model)) + 
  geom_bar(stat = "identity", color = "black", position = position_dodge()) +
  geom_errorbar(aes(ymin= LowCI, ymax = UpCI), width= 0.2, position = position_dodge(0.9)) +
  geom_hline(aes(yintercept=rho_Accu[1]), color = "purple") +
  geom_hline(aes(yintercept=rho_Accu[2]), color = "purple", linetype = "dashed") +
  geom_hline(aes(yintercept=rho_Accu[3]), color = "purple", linetype = "dashed") +
  theme_classic() + 
               labs(x = "", y = "Accuracy") +
               theme(legend.position = "right",
                     legend.title = element_blank(),
                     legend.text.align = 1) +
               scale_fill_brewer( palette = "Set1")

fig4 <- grid.arrange(fig4t, fig4b, ncol = 1, heights = c(1.7,1))

ggsave("fig4.tiff", fig4, width = 7, height = 10, units = "in", dpi = 300)

```

# Draw Figure 5 classification for E tf line, confusion matrix and accuracy bar plot
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
library(ROCR)
library(magrittr)
library(caret)
require(gridExtra)
library(reshape2)


fig5 <-list()
fig5data <- list()
levels(Etest$transgenic_line) <- levels(Etrain$transgenic_line)
Eline_name <- c("Ctgf", "Cux2","Nr5a1","Ntsr1","Rbp4","Rorb","Scnn1a-Tg2","Scnn1a-Tg3","Slc17a6")

models <- c("ANN", "reg", "rf")
input <- c("full", "long", "short", "ramp")


E.ANN.full.char <- as.character(E.ANN.full[,1]+1)
E.ANN.long.char <- as.character(E.ANN.long[,1]+1)
E.ANN.short.char <- as.character(E.ANN.short[,1]+1)
E.ANN.ramp.char <- as.character(E.ANN.ramp[,1]+1)
for(i in 1:10) {
  E.ANN.full.char[E.ANN.full.char == as.character(i)] <- as.character(levels(Etrain$transgenic_line)[i])
  E.ANN.long.char[E.ANN.long.char == as.character(i)] <- as.character(levels(Etrain$transgenic_line)[i])
  E.ANN.short.char[E.ANN.short.char == as.character(i)] <- as.character(levels(Etrain$transgenic_line)[i])
  E.ANN.ramp.char[E.ANN.ramp.char == as.character(i)] <- as.character(levels(Etrain$transgenic_line)[i])
  
  }

accu_E <- NA

for(i in 1:3) {
  if (models[i] == "ANN") {
    for(j in 1:4) {
      modelname <- paste0("E.",models[i],".",input[j],".char")
      model <- get(modelname)
      model_factor <- factor(model, levels = levels(Etrain$transgenic_line))
      cm_table <- confusionMatrix(model_factor, Etest$transgenic_line)
      fig5data[[j]] <- melt(cm_table$table)
      accu_each <- as.data.frame(cm_table$overall[c(1, 3:4)])
      accu_each <- rbind.data.frame(accu_each, models[i], input[j])
      colnames(accu_each) <- modelname
      accu_E <- cbind.data.frame(accu_E, accu_each)
      }
    }
  else {
      for(j in 1:4) {
        modelname <- (paste0("E.",models[i], ".", input[j],".nocv"))
        model <- get(modelname)
        cm_table <- confusionMatrix(predict(model, newdata = Etest), Etest$transgenic_line)
        fig5data[[j+(4*(i-1))]] <- melt(cm_table$table)
        accu_each <- as.data.frame(cm_table$overall[c(1, 3:4)])
        accu_each <- rbind.data.frame(accu_each, models[i], input[j])
        colnames(accu_each) <- modelname
        accu_E <- cbind.data.frame(accu_E, accu_each)
        }
  }
}


for(i in 1:12){
  fig5[[i]]<-ggplot(data = fig5data[[i]],aes(x=Prediction, y=Reference), fill=value) + geom_tile(aes(fill=value)) +
  scale_y_discrete(limits = rev(levels(fig5data[[i]]$Reference)), labels=rev(Eline_name), position = "right") +
  scale_x_discrete(labels=Eline_name)  +
  scale_fill_gradient2(mid = "lightgoldenrodyellow", high = "firebrick2")+geom_text(label=fig5data[[i]]$value) + theme(plot.title = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(), 
          panel.background = element_blank(), 
          legend.position = "none") 
}

fig5[[1]] <- fig5[[1]] + scale_x_discrete(position = "top") + scale_y_discrete(limits = rev(levels(fig5data[[i]]$Reference)), labels=rev(Eline_name), position = "left") + labs(x = "Full", y = "ANN") + theme(axis.title = element_text(size = rel(1.5)))
fig5[[2]] <- fig5[[2]] + scale_x_discrete(position = "top")+labs(x = "Long") + theme(axis.title = element_text(size = rel(1.5)), axis.title.y = element_blank())
fig5[[3]] <- fig5[[3]] + scale_x_discrete(position = "top")+labs(x = "Short") + theme(axis.title = element_text(size = rel(1.5)), axis.title.y = element_blank())
fig5[[4]] <- fig5[[4]] + scale_x_discrete(position = "top")+labs(x = "Ramp") + theme(axis.title = element_text(size = rel(1.5)), axis.title.y = element_blank(), axis.ticks.y.right = element_line(), axis.text.y.right = element_text(hjust=0, vjust = 0.5))

fig5[[5]] <- fig5[[5]] + scale_y_discrete(limits = rev(levels(fig5data[[i]]$Reference)), labels=rev(Eline_name), position = "left") + labs(y = "LASSO") + theme(axis.title = element_text(size = rel(1.5)), axis.title.x = element_blank())

fig5[[8]] <- fig5[[8]] + theme(axis.ticks.y.right = element_line(), axis.text.y.right = element_text(hjust=0, vjust = 0.5))

fig5[[9]] <- fig5[[9]] + scale_y_discrete(limits = rev(levels(fig5data[[i]]$Reference)), labels=rev(Eline_name), position = "left") + labs(y = "RF") + scale_x_discrete(labels=Eline_name, position = "bottom") + theme(axis.title = element_text(size = rel(1.5)), axis.title.x = element_blank(), axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90))

fig5[[10]] <- fig5[[10]] + scale_x_discrete(labels=Eline_name, position = "bottom") + theme(axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90))
fig5[[11]] <- fig5[[11]] + scale_x_discrete(labels=Eline_name, position = "bottom") + theme(axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90))

fig5[[12]] <- fig5[[12]] + scale_x_discrete(labels=Eline_name, position = "bottom") + theme(axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90), axis.ticks.y.right = element_line(), axis.text.y.right = element_text(hjust=0, vjust = 0.5))

fig5_u_grob <-lapply(fig5, ggplotGrob)
fig5_u_grob
fig5_cm <- grid.arrange(grobs = fig5_u_grob, ncol = 4, nrow = 3, heights = c(1,0.9,1.2), widths = c(1, 0.9, 0.9, 1.1))

ggsave("fig5cm.tiff", fig5_cm, width = 12, height = 7, units = "in", dpi = 300)




# Accruay bar chart, accurary date was collected above for-loop

accu_E <- cbind.data.frame(accu_E[2:13])
accu_E <- as.data.frame(t(accu_E))
colnames(accu_E) <- c("Accuracy", "LowCI", "UpCI", "Model", "Input")
accu_E$Accuracy <- as.numeric(as.character(accu_E$Accuracy))
accu_E$LowCI <- as.numeric(as.character(accu_E$LowCI))
accu_E$UpCI <- as.numeric(as.character(accu_E$UpCI))
accu_E$Input <- factor(accu_E$Input, levels(accu_E$Input)[c(1,2,4,3)]) # reorder levels of input from alphabetical to experimental, to match with previous curves
levels(accu_E$Model) <- c("ANN", "LASSO", "RF")
levels(accu_E$Input) <- c("Full", "Long", "Short", "Ramp")

fig5_b <- ggplot(data = accu_E, aes(Input, Accuracy, fill = Model)) + 
  geom_bar(stat = "identity", color = "black", position = position_dodge()) +
  geom_errorbar(aes(ymin= LowCI, ymax = UpCI), width= 0.2, position = position_dodge(0.9)) +

  theme_classic() + 
               labs(x = "", y = "Accuracy") +
               theme(legend.position = "bottom",
                     legend.title = element_blank(),
                     legend.margin=margin(t=-0.7, unit='cm'), 
                     legend.text = element_text(margin = margin(l = 5, r = 10, unit = "pt"))) +
               scale_fill_brewer( palette = "Set1")

ggsave("fig5accubar.tiff", fig5_b, width = 12, height = 7, units = "in", dpi = 300)


fig5 <- grid.arrange(fig5_cm, fig5_b, ncol = 1, heights = c(2,1))

ggsave("fig5.tiff", fig5, width = 12, height = 10, units = "in", dpi = 300)
                          
```


# Draw Figure 6 classification for I tf line, confusion matrix and accuracy bar plot
```{r, message=FALSE, warning=FALSE}
require(ggplot2)
library(ROCR)
library(magrittr)
library(caret)
require(gridExtra)
library(reshape2)


fig6 <-list()
fig6data <- list()

Iline_name <- c("Chat", "Chrna2","Gad2","Htr3a","Ndnf", "Nkx2.1","Pvalb","Sst","Vip")

models <- c("ANN", "reg", "rf")
input <- c("full", "long", "short", "ramp")


I.ANN.full.char <- as.character(I.ANN.full[,1]+1)
I.ANN.long.char <- as.character(I.ANN.long[,1]+1)
I.ANN.short.char <- as.character(I.ANN.short[,1]+1)
I.ANN.ramp.char <- as.character(I.ANN.ramp[,1]+1)
for(i in 1:10) {
  I.ANN.full.char[I.ANN.full.char == as.character(i)] <- as.character(levels(Itrain$transgenic_line)[i])
  I.ANN.long.char[I.ANN.long.char == as.character(i)] <- as.character(levels(Itrain$transgenic_line)[i])
  I.ANN.short.char[I.ANN.short.char == as.character(i)] <- as.character(levels(Itrain$transgenic_line)[i])
  I.ANN.ramp.char[I.ANN.ramp.char == as.character(i)] <- as.character(levels(Itrain$transgenic_line)[i])
  
  }

accu_I <- NA

for(i in 1:3) {
  if (models[i] == "ANN") {
    for(j in 1:4) {
      modelname <- paste0("I.",models[i],".",input[j],".char")
      model <- get(modelname)
      model_factor <- factor(model, levels = levels(Itrain$transgenic_line))
      cm_table <- confusionMatrix(model_factor, Itest$transgenic_line)
      fig6data[[j]] <- melt(cm_table$table)
      accu_each <- as.data.frame(cm_table$overall[c(1, 3:4)])
      accu_each <- rbind.data.frame(accu_each, models[i], input[j])
      colnames(accu_each) <- modelname
      accu_I <- cbind.data.frame(accu_I, accu_each)
      }
    }
  else {
      for(j in 1:4) {
        modelname <- (paste0("I.",models[i], ".", input[j],".nocv"))
        model <- get(modelname)
        cm_table <- confusionMatrix(predict(model, newdata = Itest), Itest$transgenic_line)
        fig6data[[j+(4*(i-1))]] <- melt(cm_table$table)
        accu_each <- as.data.frame(cm_table$overall[c(1, 3:4)])
        accu_each <- rbind.data.frame(accu_each, models[i], input[j])
        colnames(accu_each) <- modelname
        accu_I <- cbind.data.frame(accu_I, accu_each)
        }
  }
}


for(i in 1:12){
  fig6[[i]]<-ggplot(data = fig6data[[i]],aes(x=Prediction, y=Reference), fill=value) + geom_tile(aes(fill=value)) +
  scale_y_discrete(limits = rev(levels(fig6data[[i]]$Reference)), labels=rev(Iline_name), position = "right") +
  scale_x_discrete(labels=Iline_name)  +
  scale_fill_gradient2(mid = "lightgoldenrodyellow", high = "firebrick2")+geom_text(label=fig6data[[i]]$value) + theme(plot.title = element_blank(),
          axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(), 
          panel.background = element_blank(), 
          legend.position = "none") 
}

fig6[[1]] <- fig6[[1]] + scale_x_discrete(position = "top") + scale_y_discrete(limits = rev(levels(fig6data[[i]]$Reference)), labels=rev(Iline_name), position = "left") + labs(x = "Full", y = "ANN") + theme(axis.title = element_text(size = rel(1.5)))
fig6[[2]] <- fig6[[2]] + scale_x_discrete(position = "top")+labs(x = "Long") + theme(axis.title = element_text(size = rel(1.5)), axis.title.y = element_blank())
fig6[[3]] <- fig6[[3]] + scale_x_discrete(position = "top")+labs(x = "Short") + theme(axis.title = element_text(size = rel(1.5)), axis.title.y = element_blank())
fig6[[4]] <- fig6[[4]] + scale_x_discrete(position = "top")+labs(x = "Ramp") + theme(axis.title = element_text(size = rel(1.5)), axis.title.y = element_blank(), axis.ticks.y.right = element_line(), axis.text.y.right = element_text(hjust=0, vjust = 0.5))

fig6[[5]] <- fig6[[5]] + scale_y_discrete(limits = rev(levels(fig6data[[i]]$Reference)), labels=rev(Iline_name), position = "left") + labs(y = "LASSO") + theme(axis.title = element_text(size = rel(1.5)), axis.title.x = element_blank())

fig6[[8]] <- fig6[[8]] + theme(axis.ticks.y.right = element_line(), axis.text.y.right = element_text(hjust=0, vjust = 0.5))

fig6[[9]] <- fig6[[9]] + scale_y_discrete(limits = rev(levels(fig6data[[i]]$Reference)), labels=rev(Iline_name), position = "left") + labs(y = "RF") + scale_x_discrete(labels=Iline_name, position = "bottom") + theme(axis.title = element_text(size = rel(1.5)), axis.title.x = element_blank(), axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90))

fig6[[10]] <- fig6[[10]] + scale_x_discrete(labels=Iline_name, position = "bottom") + theme(axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90))
fig6[[11]] <- fig6[[11]] + scale_x_discrete(labels=Iline_name, position = "bottom") + theme(axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90))

fig6[[12]] <- fig6[[12]] + scale_x_discrete(labels=Iline_name, position = "bottom") + theme(axis.ticks.x= element_line(), axis.text.x = element_text(hjust=1, vjust = 0.5, angle = 90), axis.ticks.y.right = element_line(), axis.text.y.right = element_text(hjust=0, vjust = 0.5))

fig6_u_grob <-lapply(fig6, ggplotGrob)
fig6_u_grob
fig6_cm <- grid.arrange(grobs = fig6_u_grob, ncol = 4, nrow = 3, heights = c(1,0.9,1.2), widths = c(1, 0.9, 0.9, 1.1))

ggsave("fig6cm.tiff", fig6_cm, width = 12, height = 7, units = "in", dpi = 300)




# Accruay bar chart, accurary date was collected above for-loop

accu_I <- cbind.data.frame(accu_I[2:13])
accu_I <- as.data.frame(t(accu_I))
colnames(accu_I) <- c("Accuracy", "LowCI", "UpCI", "Model", "Input")
accu_I$Accuracy <- as.numeric(as.character(accu_I$Accuracy))
accu_I$LowCI <- as.numeric(as.character(accu_I$LowCI))
accu_I$UpCI <- as.numeric(as.character(accu_I$UpCI))
accu_I$Input <- factor(accu_I$Input, levels(accu_I$Input)[c(1,2,4,3)]) # reorder levels of input from alphabetical to experimental, to match with previous curves
levels(accu_I$Model) <- c("ANN", "LASSO", "RF")
levels(accu_I$Input) <- c("Full", "Long", "Short", "Ramp")

fig6_b <- ggplot(data = accu_I, aes(Input, Accuracy, fill = Model)) + 
  geom_bar(stat = "identity", color = "black", position = position_dodge()) +
  geom_errorbar(aes(ymin= LowCI, ymax = UpCI), width= 0.2, position = position_dodge(0.9)) +

  theme_classic() + 
               labs(x = "", y = "Accuracy") +
               theme(legend.position = "bottom",
                     legend.title = element_blank(),
                     legend.margin=margin(t=-0.7, unit='cm'), 
                     legend.text = element_text(margin = margin(l = 5, r = 10, unit = "pt"))) +
               scale_fill_brewer( palette = "Set1")

ggsave("fig6accubar.tiff", fig6_b, width = 12, height = 7, units = "in", dpi = 300)


fig6 <- grid.arrange(fig6_cm, fig6_b, ncol = 1, heights = c(2,1))

ggsave("fig6.tiff", fig6, width = 12, height = 10, units = "in", dpi = 300)
```


